The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2016-11-18 manuscript/manuscript.Rnw
rewrite abstract

  \textbf{Method} Using RNA-seq, we measured the expression profiles
  of \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals.

  \textbf{Results} We identified a set of
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  core genes which are expressed (FPKM $\ge 10$) in all placentas,

  including genes with immune-modulating properties (\textit{ANXA2},
  \textit{ANXA1}, \textit{S100A11}, and \textit{S100A10}), cell-cell
  interactions (\textit{LAMC1}, \textit{LUM}, and \textit{LGALS1}),
  and trophoblast fusion (\textit{ANXA5} and \textit{ANXA1}).

  \textbf{Discussion}

  Still, using the strictest filtering strategy
  we find a core set of only
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  genes is essential for the proper functioning of the placenta in all
  species analyzed.

>>>>

  \textbf{Method} Using RNA-seq, we measured the expression profiles
  of \Sexpr{star.logs[,length(unique(file))]} term placentas of
  \Sexpr{star.logs[,length(unique(species))]} species of mammals, and
  compared the evolution of expression across clades.

  \textbf{Results} We identified a set of
  \Sexpr{core.placenta.transcriptome.long[housekeeping==FALSE,length(unique(human_name))]}
  core genes which are expressed (FPKM $\ge 10$) in all placentas, %
  %
  including genes with immune-modulating properties (\textit{ANXA2},
  \textit{ANXA1}, \textit{S100A11}, and \textit{S100A10}), cell-cell
  interactions (\textit{LAMC1}, \textit{LUM}, and \textit{LGALS1}),
  invasion (\textit{GRB2} and \textit{RALB5}) and trophoblast fusion
  (\textit{ANXA5} and \textit{ANXA1}). %
  We also identified multiple pre-eclampsia associated genes which are
  differentially expressed in \textit{Homo sapiens} when compared to
  the other %
  \Sexpr{star.logs[,length(unique(species))-1]} species. %

  \textbf{Discussion} %
  Using the strictest filtering strategy we find a core set of only
  \Sexpr{core.placenta.transcriptome.long[housekeeping==FALSE,length(unique(human_name))]}
  genes is essential for the proper functioning of the placenta in all
  species analyzed. We also found significantly higher expression of
  the pre-eclampsia associated genes \textit{KISS1}, \textit{CRH},
  \textit{PAPPA}, and \textit{ADAM12} on the \human lineage.
